### 2016-05-09 README.Rmd
fix #527 ion() removed marked as defunct updated cran comments and started to update news bumped to ver to push to cran updated readme

[![Build Status](https://api.travis-ci.org/ropensci/taxize.png?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![codecov.io](https://codecov.io/github/ropensci/taxize/coverage.svg?branch=master)](https://codecov.io/github/ropensci/taxize?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/taxize)](http://cran.rstudio.com/web/packages/taxize)

@@

	<td style="text-align:left;">Index of Names (ION)</td>
	<td style="text-align:left;"><code>ion</code></td>
	<td style="text-align:left;"><a href="http://www.organismnames.com/">link</a></td>

@@

**: There are none! We suggest using `TPL` and `TPLck` functions in the [taxonstand package](https://cran.rstudio.com/package=Taxonstand). We provide two functions to get bullk data: `tpl_families` and `tpl_get`.

>>>>

[![Build Status](https://api.travis-ci.org/ropensci/taxize.png?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![codecov.io](https://codecov.io/github/ropensci/taxize/coverage.svg?branch=master)](https://codecov.io/github/ropensci/taxize?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

@@

**: There are none! We suggest using `TPL` and `TPLck` functions in the [taxonstand package](https://cran.r-project.org/package=Taxonstand). We provide two functions to get bullk data: `tpl_families` and `tpl_get`.
